---
title: "A brief introduction to tpotr"
author: "Thorben Hellweg"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette: 
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# A gentle introduction
The **tpotr** package, *Tree-based Pipeline Optimization Tool in R*, is conceived as a "Data Science Assistant" to automate the most tedious part of machine learning: Finding the best pipeline for your data.

The **tpotr** package enables you to use the well known python based **tpot** module in your favourite programming language R. TPOT intelligently explores thousands of possible machine learning pipelines by using genetic programming. Once finished, the fitted pipeline can be accessed in R and used for prediction.

The best way to illustrate the process of fitting a machine learning pipeline in **tpotr** is by example. Assume the goal is to find a pipeline for the well known iris dataset. We first split the dataset to get one for training and one for validation purposes:
```{r setup}
library(tpotr)
```
```{r}
data(iris)
# 75% of the sample size
smp_size <- floor(0.75 * nrow(iris))

# set the seed to make your partition reproducible
set.seed(123)
train_ind <- sample(seq_len(nrow(iris)), size = smp_size)

train <- iris[train_ind, ]
test <- iris[-train_ind, ]
train[5] <- as.numeric(train[[5]])
test[5] <- as.numeric(test[[5]])
```
The iris dataset holds 150 observations with 5 features. We will use the first 4 features to predict the 5th, the species. As this is a classification task, we use a TPOTRClassifier to fit a pipeline:
```{r}
library(tpotr)
classifier <- TPOTRClassifier(verbosity=2, generations = 5, population_size=15, n_jobs = 3)
tpotr::fit(classifier, train[1:4], train[5])
```
You can now use the fitted pipeline for predictions. To assess the accurancy of the predictions, the score() method can be used.
```{r}
predict(classifier, test[1:4])
score(classifier, test[1:4], test[5])
```
